### 2020-03-30 reviews/SIGBOVIK_2020_review_13.tex
reviews: Reformat review

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Michael Coblenz}
\rating{Objection}
\confidence{Your Honor}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{37}
\papertitle{The Pacman effect and the Disc-Sphere Duality}

@@

%%% Replace the following text with your review.
I’m afraid I must object to triple-blind review on the grounds that it, too, may be biased because the
reviewers still know they are reviewers. Have you considered quadruple-blind review, in which reviews are
elicited from reviewers without informing them that they are writing reviews?

>>>>

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Exponentiator}
\rating{Better and better every day, by leaps and bounds and\\\qquad\quad\; leaping leaps and bounding bounds}
\confidence{Those guys have faith, why shouldn't I?}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{NN}
\papertitle{UNKNOWN PAPER TITLE}

@@

%%% Replace the following text with your review.
\center\includegraphics[height=5in]{walk-to-sky-exp}
